Lens Modeling in \sw

### 2013-09-09 text/tex/results.tex
t1

We conclude that the volunteers are performing very well identifying images and putting them approximately at the right spot (test 1), with a performance of 92\%.
Most of the problems where due to unclear arc-like structures (Error 1, p=0.18; Error 4, p=0.03; Error 8, p=0.04).
Critical failures like the failure to identify all fife images in an fife image system (Error 3, p=0.04) or to include too many images (Error 10, p=0.01) did almost never happend.
From this we conclude that the introduction materials was adequate and the volunteers got the basics of gravitational lensing.

@@

>>>>

We conclude that the volunteers are performing very well identifying and positioning images (T1a), with a performance of 92\% (approxPlace p=0.92).
Most of the problems where due to unclear arc-like structures (Error 1, p=0.18; Error 4, p=0.03; Error 8, p=0.04).
Critical failures like the failure to identify all fife images in an fife image system (Error 3, p=0.04) or to include too many images (Error 10, p=0.01) did almost never happend.
From this we conclude that the introduction materials was adequate and the volunteers got the basics of gravitational lensing.

@@

Error 5 and 6 happen mostly in very symetric images, where it's hard to tell
It changes the orientation of the mass distribution.
But kappa encl and thus the einsteinradius is not changed, and thus the final result is still a valid model.
